% !TEX spellcheck = English (United States) (Aspell)
% !TEX TS-program = arara
%  arara: lmkclean
%  arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
%  arara: biber
%  arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
%  arara: pdflatex: { synctex: yes, options: '-file-line-error -halt-on-error' }
%  arara: lmkclean
\documentclass[crop=false,float=true,class=scrreprt]{standalone}

\providecommand{\main}{../..}
\input{\main/Subfiles/0-Preamble/0-Preamble.tex}  % Preamble [document configuration]

\begin{document}

\section{Future work}
\label{SEC:conclusions:futureWork}

The following is a non-comprehensive list of potential future work 
which could be performed to improve the capabilities of the test platform
or supplement the control studies already performed on the test platform.


% NOTE: Consider providing section links to relevant information.


\begin{itemize}[leftmargin=*]

\item Optimize sample interval of hardware.
\begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
    
  \item Determine limiting factors in the reduction of the board sampling interval.
  
  \item Improve upon these factors, if possible.
  
  \item Determine alternative model algorithms such that processing {\fns(\tif{per sample interval)}} is significantly minimized.\\
        {\fns[\tif{Example: Use binary classes wherever possible.}]}
  
\end{itemize}


\item Optimize serial communication.
\begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]

  \item Implement bluetooth wireless transmission.

  \item Determine limiting factors in the reduction of the serial transmission interval.
  \begin{itemize}[leftmargin=*, label=$\cdot$]
  
    \item Determine if increasing the serial communication sample interval improves limits on hardware sample interval.\\
          {\fns\tif{This is already performed when sending a high number of signals, \\
                    but improved performance has not been verified.}}
    
    \item Determine if increasing the BAUD frequency on the board will remove limits on the serial transmission interval.
    
  \end{itemize}
    
  \item Determine how to begin a read without resetting the hardware.
  
  \item Determine if dynamic/real-time plotting is worthwhile. If so, implement.
  
\end{itemize}




\clearpage




\item Implement alternate linear controllers.
\begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]

  \item Implement pole-placement controller(s).
  
  \item Implement LQG controller(s).
  
  \item Implement $H_{N}$ controller(s).
        \hspace*{\fill}{\fns[\tif{Where $N$ is an integer or infinity.}]}

\end{itemize}


\item Implement a nonlinear plant model.
\begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]

  \item Develop nonlinear controller(s).
  
  \item Demonstrate operation in nonlinear states.\\
        {\fns\tif{Example: Operating in a state with a significantly increased component of horizontal pitch.}}

\end{itemize}


\item Improve model parameters measurements.
\begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]

  \item Improve mass measurements.
  \begin{itemize}[leftmargin=*, label=$\cdot$]
  
    \item Use scale with improved precision.
          \hspace*{\fill}{\fns[\tif{Current precision is 0.01 [lb].}]}
  
  \end{itemize}
  
  \item Improve motor transfer function measurement. 
        \hspace*{\fill}{\fns[\tif{Angular velocity vs. Input Voltage}]}\\
        {\fns\tif{Hardware must remain perfectly upright while in motion to perform this measurement.\\
        The original measurement was taken while balancing the in-motion device by hand.\\
        Since a pitch controller has been developed, the measurement may be taken more accurately.}}

  \item Verify conflicting motor parameters derived from References \cite{REF:conference:2015-howard}, \cite{REF:online:philohome}:
  \begin{itemize}[leftmargin=*, label=$\cdot$]
  
    \item \tif{Resistance, $R_{mtr}$}
  
    \item \tif{Torque   constant, $k_{mtr.T}$}
    
    \item \tif{Back EMF constant, $k_{mtr.bEMF}$}
  
  \end{itemize}
  
\end{itemize}

\item Increase MinSeg power-source voltage-maximum.
      \hspace*{\fill}{\fns[\tif{See Section~%
                                \ref{SEC:preliminaryDecisions:selectionHardwareSoftware:hardware:components:motorDriver}.%
                                }]}\\[+0.5em]
      {\small
      \begin{tabular}{l @{\ } c @{\ } c}
      Current voltage source maximum: & $09$ & [V].\\
      Motor driver operating maximum: & $36$ & [V].
      \end{tabular}
      }




\clearpage




\item Construct alternate physical models via simple variants.
\begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]

  \item Alternate mass distribution.
  \begin{itemize}[leftmargin=*, label=$\cdot$]
  
    \item Reduce number of batteries to less than 6.
          \hspace*{\fill}{\fns[\tif{Requires use of USB cable for power.}]}
  
  \end{itemize}
  
  \item Alternate geometry.
  \begin{itemize}[leftmargin=*, label=$\cdot$]
  
    \item Alternate wheel component.\\
          \hspace*{\fill}{\fns[\tif{Search for Lego tires with differing radius, mass, and/or coefficient of friction. 
                                    See \cite{REF:online:legoWheels}}]}
    
    \item Incorporation of a second mass on the pendulum.
  
  \end{itemize}
  
\end{itemize}


\item Perform movement on an uneven surface.


\item Optimize filter design.
\begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]

  \item Determine tradeoffs between no filter vs 1$^{\text{st}}$ to 6$^{\text{th}}$ order bessel filters.
  
  \item Determine tradeoffs between state-space and transfer function blocks, if any.
  
  \item Determine tradeoffs between Matlab besself and bessel poles, if any?

\end{itemize}


\item Optimization of observable data
\begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]

  \item Implement voltage sensor across battery holster.\\
        Use this voltage reading to determine the true voltage of the power source in operation.

  \item Incorporate use of accelerometer?\\
        Incorporate use of Kalman filter?\\
        Compare effects.
  
\end{itemize}




\clearpage




\item Test Windows and Linux compatibility.
      \hspace*{\fill}{\fns[\tif{Document necessary changes, if any.}]}


\item Improve overrun detection.\\
      {\fns\tif{If the board cannot complete all of its processes before the sampling interval completes,\\
                then it performs incorrectly. Detection of this is possible and desirable for the user.\\
                Currently, overrun detection requires that the the user manually view an LED on the board.\\
                The LED is very small and almost entirely masked by the bluetooth module.\\
                (Simulink also currently prevents status reads of the overrun LED pin.)\\
                An alternative method should exist which alert the user more conveniently.}}

\end{itemize}




\clearpage




\end{document}










