%!!TEX root = ../../2016.02.08_Kando_Thesis.tex
% !TEX spellcheck = English
% !TEX TS-program = arara
%  arara: lmkclean
% !arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
% !arara: bibtex
% !arara: biber
%  arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
%  arara: pdflatex: { synctex: yes, options: '-file-line-error -halt-on-error' }
%  arara: lmkclean
\documentclass[crop=false,float=true,class=scrreprt]{standalone}

\providecommand{\main}{../..}
\input{\main/Subfiles/0-Preamble/0-Preamble.tex}  % Preamble [document configuration]

\begin{document}

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}


This thesis develops a test platform for a control problem.

The inverted pendulum is selected as a well-established control problem.
It is representative of an unstable nonlinear system
which may remain balanced using any of several methods. 
Once balancing is achieved, 
multidimensional maneuvering is added as a supplemental control objective.

To approach the control problem hardware is selected
which is then characterized and simulated, 
and then operated while communicating operational data.

The thesis provides a detailed description of the approaches to:

\begin{itemize}[leftmargin=*]
\item Selecting the hardware.
\item Characterizing the hardware.
\item Developing a functioning controller.
\item Simulating the results.
\end{itemize}

Additionally, a modular test platform is developed 
such that additional control approaches
or characterization models could be implemented and hot-swapped.

\clearpage



\end{document}









