% !TEX spellcheck = English (United States) (Aspell)
% !TEX TS-program = arara
%  arara: clean   : { extensions: [aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml] }
% !arara: pdflatex: {               options: ['-file-line-error','-halt-on-error','-ini','"&pdflatex"','mylatexformat.ltx'] }
% !arara: pdflatex: {   draft: yes, options: ['-file-line-error','-halt-on-error','-fmt=mylatexformat'] }
% !arara: biber
%  arara: pdflatex: {   draft: yes, options: ['-file-line-error','-halt-on-error','-fmt=mylatexformat'] }
%  arara: pdflatex: { synctex: yes, options: ['-file-line-error','-halt-on-error','-fmt=mylatexformat'] }
%  arara: clean   : { extensions: [aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml] }
\documentclass[crop=false,float=true,class=scrreprt]{standalone}

\providecommand{\main}{../..}
\input{\main/Subfiles/0-Preamble/0-Preamble.tex}  % Preamble [document configuration]

\begin{document}

\chapter{Introduction}





\section{Purpose}

The intent of this thesis is as follows:

\begin{enumerate}[leftmargin=*]

\item Establish Control Problem

\begin{enumerate}[leftmargin=*]                                                                        \vspace{-1em}
      
  \item Select a well-established control problem as a focal point.                                   %\\
  \hspace*{\fill}{\fns[\tif{Inverted Pendulum: Two-wheeled Robot}]}                                   %\vspace{-1em}
      
\end{enumerate}                                                                                        \vspace{-0.5em}
      
\item Establish Plant

\begin{enumerate}[leftmargin=*]                                                                        \vspace{-1em}
      
  \item Select and derive equations for a physical dynamics model associated with the control problem. \\
        \hspace*{\fill}{\fns[\tif{\textcite{REF:online:2009-yamamoto}}]}                               \vspace{-1em}

  \item Select real-world hardware which parallels the selected physical dynamics model.
        \hspace*{\fill}{\fns[\tif{MinSeg M2V5}]}                                                       \vspace{-1em}

  \item Characterize the selected hardware to populate the physical dynamics equations.               %\vspace{-1em}
      
\end{enumerate}                                                                                        \vspace{-0.5em}

\item Establish Controller

\begin{enumerate}[leftmargin=*]                                                                        \vspace{-1em}

  \item Select and derive controller design(s) to address the selected control problem.               %\\
        \hspace*{\fill}{\fns[\tif{Optimal Controller}]}                                                \vspace{-1em}
      
  \item Select introductory gains to populate the selected controller design equations.               %\vspace{-1em}
      
\end{enumerate}                                                                                        \vspace{-0.5em}

\item Establish Test Platform {\fns(\tif{for Simulation and Actuation})}

\begin{enumerate}[leftmargin=*]                                                                        \vspace{-1em}

  \item Select an integrated development environment (IDE).                                           %\\
        \hspace*{\fill}{\fns[\tif{Mathworks Software Suite}]}                                          \vspace{-1em}

      
  \item Develop a robust test software platform on the selected IDE which is able to:
  
  \begin{itemize}[leftmargin=*]                                                                        \vspace{-1em}

    \item Model established plant      in simulation.                                                  \vspace{-1em}
    \item Model established controller in simulation \tbf{and} in real-time.                           \vspace{-1em}
    \item Program selected real-world hardware prior to operation.                                     \vspace{-1em}
    \item Communicate with selected real-world hardware during/after operation.                       %\vspace{-1em}
      
  \end{itemize}                                                                                        \vspace{-0.5em}
                                                                                                      %\vspace{-1em}

\end{enumerate}                                                                                        \vspace{-0.5em}

\item Execute Testing

\begin{enumerate}[leftmargin=*]                                                                        \vspace{-1em}

  \item Determine idealized  controller equation parameters via simulation testing/post-processing.    \vspace{-1em}
  \item Determine actualized controller equation parameters via real-time  testing/post-processing.   %\vspace{-1em}
  
\end{enumerate}                                                                                        \vspace{-0.5em}

\end{enumerate}




\clearpage




\section{Statement of the Problem}

The two-wheeled robot is a well-established control problem.  
The robot is topheavy and must continually work to balance itself.
The robot is able to move freely on a two-dimensional plane; however,
any movements performed by the robot create additional disturbances
against its ability to balance itself.

%\section{Statement of the Problem}

Numerous command regulator approaches {\fns(\tif{PID, pole-placement, optimal})} 
have been developed to control such a device;
however, no one approach has been determined as a clear choice.
Additional functionalities other than command regulators 
which significantly improve performance
may also be implemented in a controller.

This study therefore intends to comparatively study 
multiple control approaches involving optimal-control-focused command regulators
and to study the effects of additional functionalities which may be beneficial in general control cases.
As a prerequisite to this work, a test platform must be developed for which to design the controllers.
This study intends to design the test platform such that:

\vspace{-0.5em}

\begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]

\item Studies could be performed in simulation {\fns\tif{(using a hardware-equivalent model)}}.

\item Studies could be performed on actual hardware.

\item Similar work involving alternate control methods could easily be incorporated on both.

\end{itemize}

\vspace{-0.5em}

The intent of the latter is to significantly diminish
several barriers to entry to perform a control study relating to hardware 
{\fns\tif{(initial implementation, interfacing/communication, and theoretical/simulation modeling)}}.
This would ideally encourage future studies 
as well as draw them to a common platform,
which would allow for effective comparisons between those studies.




\clearpage




\section{Methodology}

The methodology of this thesis is as follows:

\begin{enumerate}[leftmargin=*]

\item Select a well-established control problem as a focal point.
\hspace*{\fill}{\fns[\tif{Inverted Pendulum: Two-wheeled Robot}]}\\[-2.0em]
\begin{itemize}[leftmargin=*]

  \item Select compatible hardware and software.
  \hspace*{\fill}{\fns$
  \begin{bmatrix}
  \text{HW: \tif{MinSeg (Two-Wheeled Robot)}  }\\ 
  \text{SW: \tif{Mathworks Matlab \& Simulink}}\\
% \text{SW: \tif{RPI (J Hurst) MinSeg drivers}}\\
  \end{bmatrix}
  $}
  
  \item Implement basic hardware-software interfaces.
% \hspace*{\fill}{\fns[\tif{RPI Mechatronics Labs}]}\\[-2.0em]
  \begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
    
    \item Process signals input to hardware drivers.
    \item Process raw signals output from hardware sensors.\\[-5.5em]
    \hspace*{\fill}{\fns$
    \begin{bmatrix}
    \text{\tif{Datatype conversion   }}\\
    \text{\tif{Unit     conversion   }}\\
    \text{\tif{Derivation/Integration}}\\ 
    \text{\tif{Filtration            }}\\
    \end{bmatrix}
    $}\\[-1.0em]
      
  \end{itemize}
  
\end{itemize}

%Develop a modular test platform through which varying control studies could be performed seamlessly.
%\hspace*{\fill}{\fns[\tif{In simulation and in real-time.}]}\\[-2.0em]

\item Develop a modular test platform.
\begin{itemize}[leftmargin=*]

  \item Establish infrastructure.
  \begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]

    \item Develop a unified, modular Simulink model which is capable of representing any desired system configuration.
    \hspace*{\fill}{\fns[\tif{Variant subsystems used.}]}
    
    \item Create a Matlab script hierarchy which is able to:
    \begin{itemize}[leftmargin=*, label=$\cdot$]
    
      \item Configure the Simulink model to any desired system configuration.
      
      \item Configure the Simulink model to any desired build/run state.
      
      \item Organize the relatively large number of parameters involved in such a system. 
      
      \item Minimize the effort required for the user to incorporate additional system configurations.
    
      \item Minimize the effort required for the user to transition between any system configurations.
%     \hspace*{\fill}{\fns[\tif{All user-input options localized to one section.}]}
    
    \end{itemize}
        
  \end{itemize}
  
  \item Establish robust methods of signal routing.
  \begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
  
    \item Implement bus structures.

    \item Implement serial communication between hardware and development computer.
    \begin{itemize}[leftmargin=*, label=$\cdot$]
    
      \item Minimimize sampling interval within the limits of the board hardware.
      
      \item Process transmitted signals prior to sending and reconstruct after receiving.
    
    \end{itemize}
    
  \end{itemize}



  
  
  \clearpage
  
  
  

  \item Calibrate hardware sensors.
  \begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
  
    \item Mitigate gyroscope bias.
  
  \end{itemize}

  \item Develop theoretical plant model.
  \begin{itemize}[leftmargin=*, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
    
    \item Research (non-linear) physical equations.
    
    \item Linearize the physical equations.
    \begin{itemize}[leftmargin=*, label=$\cdot$]
    
      \item Develop a state-space model.
    
    \end{itemize}
    
    \item Acquire linear plant model parameters.
    
    \item Implement linear plant model into unified test platform.
    
  \end{itemize}
  
\end{itemize}
  
\item Design and develop and controller for the test platform.
\begin{itemize}[leftmargin=*, label=$\cdot$]

  \item Implement dynamic reference tracking to mitigate bias on the body angular velocity $\phi$ sensors.
  
  \item Determine control gains using LQR.
  
\end{itemize}

\end{enumerate}




\clearpage




\printbibliography[segment=\therefsegment, heading=subbibnumbered, title={Bibliography}]




\clearpage



\end{document}










