% !TEX TS-program = arara
%  arara: lmkclean
%  arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
%  arara: biber
%  arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
%  arara: pdflatex: { synctex: yes, options: '-file-line-error -halt-on-error' }
%  arara: lmkclean
\documentclass[crop=false,float=true,class=scrreprt]{standalone}

\providecommand{\main}{../../../..}
\input{\main/Subfiles/0-Preamble/0-Preamble.tex}  % Preamble [document configuration]

\begin{document}

\subsection{Tracking System}
\label{SEC:controllerDesign:additionalDynamics:trackingSystem}

Additional dynamics may be incorporated to improve reference tracking.
When implemented for this purpose, the additional dynamics are known as a tracking system.

In the case of a tracking system, 
an \tif{integrator} may be implemented as the additional dynamics
to track a constant reference exactly, or 
to track a slowly varying reference approximately.

Integrators are also able to mitigate constant disturbances.
Incidentally, the MinSeg M2V3 system uses gyroscopes as body angular velocity $\psi$ sensors.
Bias is inherent in the output of a gyroscope;
therefore, the use of such an integrator as a tracking system has an additional benefit:
it will mitigate the effects of bias from a gyroscope output, 
whether directly or within terms which are derivative of the gyroscope output.

Thus, in the case of the two-wheeled robot, 
integrators are implemented as additional dynamics for the states representing 
wheel angular position $\theta$ and body angular position (yaw) $\phi_{y}$.
This establishes a tracking system, {\fns[\tif{an augmented method of state feedback regulation}]}, for the system.
The state-space representation of the integrator is exhibited in Equation~%
\eqref{EQN:controllerDesign:additionalDynamics:trackingSystem:integrator:analog}.

\vspace{-0em}

\begin{equation}
\label{EQN:controllerDesign:additionalDynamics:trackingSystem:integrator:analog}
\begin{array}{ccccccccc}
\uns{\mbf{\dot{x}}(t)}{n x 1}
& = &
\begin{bmatrix}
0 & 0 \\
0 & 0 \\
\end{bmatrix}
& \cdot &
\uns{\mbf{x}(t)}{n x 1} 
& + & 
\begin{bmatrix}
1 & 0 \\
0 & 1 \\
\end{bmatrix}
& \cdot &
\begin{bmatrix}
e_{\theta_{\hphantom{y}}} (t) \\
e_{\phi_{y}}              (t) \\
\end{bmatrix}
\\[+2em]
\uns{\mbf{y}(t)}{m x 1}
& = &
\begin{bmatrix}
1 & 0 \\
0 & 1 \\
\end{bmatrix}
& \cdot &
\uns{\mbf{x}(t)}{n x 1}
& + &
\begin{bmatrix}
0 & 0 \\
0 & 0 \\
\end{bmatrix}
& \cdot &
\begin{bmatrix}
e_{\theta_{\hphantom{y}}} (t) \\
e_{\phi_{y}}              (t) \\
\end{bmatrix}
\end{array}
\end{equation}




\clearpage




\subsubsection{Discrete Additional Dynamics}


Since the additional dynamics will be processed on a microcontroller,
the additional dynamics will be digital;
thus, a continuous-to-discrete conversion will be necessary.
A digital integrator is an established case which is exhibited in Equation~%
\eqref{EQN:controllerDesign:additionalDynamics:trackingSystem:integrator:discrete}.

\vspace{-0em}

\begin{equation}
\label{EQN:controllerDesign:additionalDynamics:trackingSystem:integrator:discrete}
\begin{array}{ccccccccc}
\uns{\mbf{\dot{x}}[k+1]}{n x 1}
& = &
\begin{bmatrix}
1 & 0 \\
0 & 1 \\
\end{bmatrix}
& \cdot &
\uns{\mbf{x}[k]}{n x 1}
& + & 
\begin{bmatrix}
1 & 0 \\
0 & 1 \\
\end{bmatrix}
& \cdot &
\begin{bmatrix}
e_{\theta_{\hphantom{y}}} [k] \\
e_{\phi_{y}}              [k] \\
\end{bmatrix}
\\[+2em]
\uns{\mbf{y}[k]}{m x 1}
& = &
\begin{bmatrix}
1 & 0 \\
0 & 1 \\
\end{bmatrix}
& \cdot &
\uns{\mbf{x}[k]}{n x 1}
& + &
\begin{bmatrix}
0 & 0 \\
0 & 0 \\
\end{bmatrix}
& \cdot &
\begin{bmatrix}
e_{\theta_{\hphantom{y}}} [k] \\
e_{\phi_{y}}              [k] \\
\end{bmatrix}
\end{array}
\end{equation}




\clearpage




\end{document}










