% !TEX TS-program = arara
%  arara: lmkclean
%  arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
%  arara: biber
%  arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
%  arara: pdflatex: { synctex: yes, options: '-file-line-error -halt-on-error' }
%  arara: lmkclean
\documentclass[crop=false,float=true,class=scrreprt]{standalone}

\providecommand{\main}{../..}
\input{\main/Subfiles/0-Preamble/0-Preamble.tex}  % Preamble [document configuration]

\begin{document}

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

The research performed and described in this document 
could not have been completed
without the insight and guidance of several parties.

First and foremost,
I would like to acknowledge Professor Richard J. Vaccaro
for his capabilities, his mentorship, and his professionalism in the STEAM fields community.
The great level of knowledge which he has provided to me and countless others,
{\fns\tif{whether in academic text, course lecture, personal conversation, or penned scrawl on scrap paper}},
is not to be underestimated.

Additional acknowledgement should be provided to
Professor Joshua Hurst,
who publicly released software drivers for the MinSeg hardware,
and who extended the supported platforms of those drivers
to make them accessible beyond their original use.

I would like to thank all other cited academic parties, particularly, {\fns[\tif{but in no particular order}]}:

\begin{itemize}[leftmargin=*, itemsep=-1em,label=$\cdot$]
\item Yorihisa Yamamoto, for his two-wheeled robot dynamic model.
\item "Phil O", Ryo Watanabe, and related peers, for their NXT motor studies.
\item Mike Peltier, for his two-wheeled robot control publication
\item Brian Howard and Linda Bushnell, for their MinSeg publication
\end{itemize}

Thank you for making your works available.

Finally, but of no less consideration, I would like to thank
Holly Gaboriault
who took photos on request, as well as
the members of the Wikimedia Foundation, and
the Stackexchange and Matlab Central communities,
who offered their multidisciplinary expertise regarding any number of subjects,
{\fns\tif{whether mathematical, technical, typographical, or otherwise}}, rapidly and on-demand.

\end{document}









