% !TEX spellcheck = English (United States) (Aspell)
% !TEX TS-program = arara
%  arara: lmkclean
%  arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
%  arara: biber
%  arara: pdflatex: {   draft: yes, options: '-file-line-error -halt-on-error' }
%  arara: pdflatex: { synctex: yes, options: '-file-line-error -halt-on-error' }
%  arara: lmkclean
\documentclass[crop=false,float=true,class=scrreprt]{standalone}

\providecommand{\main}{../../../..}
\input{\main/Subfiles/0-Preamble/0-Preamble.tex}  % Preamble [document configuration]

\begin{document}




\subsection{Development PC}
\label{SEC:preliminaryDecisions:selectHardware:developmentPC}

Designations pertaining to the development PC
with respect to the test platform
are exhibited in Table~%
\ref{TAB:testPlatform:developmentPC}.


\vspace*{\fill}
\begin{table}[H]
\centering%
\small%
\caption[{[Selection of Compatible HW \& SW]: Development PC Specifications}]%
        {{[Selection of Compatible HW \& SW]: Development PC Specifications~%
           \cite{REF:online:powerstream:batteryDrainage}%
           \label{TAB:testPlatform:developmentPC}%
        }}%
\begin{tabular}{ | l | c | }                                                                                 \hline & \\[-2.0em]
\tbf{Hardware}                                       & \tbf{Version}                              \\[+0.0em] \hline & \\[-2.0em]
PC                                                   & 2015 Macbook Pro 
                                                       \cite{REF:online:everymac:macbookpro:2015} \\[+0.0em] \hline
\mc{2}{c}{}                                                                                       \\[-1.0em] \hline   \\[-2.0em]
\tbf{Software}                                       & \tbf{Version}                              \\[+0.0em] \hline & \\[-2.0em]
Operating System (OS)                                & macOS 10.12.5                              \\[+0.0em] \hline & \\[-2.0em]
%%
\begin{tabular}{@{}l@{}}
Mathworks Software Suite                             \\
$\cdot$ \tif{MATLAB}                                 \\
$\cdot$ \tif{Simulink}                               \\
$\cdot$ \tif{Control System Toolbox}                 \\
$\cdot$ \tif{DSP System Toolbox}                     \\
$\cdot$ \tif{Instrument Control Toolbox}             \\
$\cdot$ \tif{MATLAB Coder}                           \\
$\cdot$ \tif{Simulink Coder}                         \\
$\cdot$ \tif{Simulink Desktop Real-Time}             \\[+1em]
$\cdot$
\tif{Matlab   Support Package for Arduino Hardware}  \\
$\cdot$
\tif{Simulink Support Package for Arduino Hardware}  \\
\end{tabular}                                        &
\begin{tabular}{@{}c@{}}
r2017a                                               \\
-                                                    \\
-                                                    \\
-                                                    \\
-                                                    \\
-                                                    \\
-                                                    \\
-                                                    \\
-                                                    \\[+1em]
17.1.0                                               \\
17.1.0                                               \\
\end{tabular}                                                                                     \\[+0.0em] \hline & \\[-2.0em]
%%
Xcode
\hspace*{\fill}{\fns
[\tif{A Mathworks (macOS)-Supported Compiler
\cite{REF:online:mathworks:supportedCompilers}.}]}    & 7.3.1                                      \\[+0.0em] \hline & \\[-2.0em]
%%
\begin{tabular}{@{}l@{}}
Rensselaer Arduino Support Package Library (RASPLib)
\hspace*{+4em}                                       \\
\hspace*{\fill}{\fns
[\tif{A third-party Simulink Support Package for MinSeg Hardware
\cite{REF:online:hurst:minsegDrivers}.}]}    
\end{tabular}                                        &
\begin{tabular}{@{}c@{}}
1.1                                                  \\
\end{tabular}                                                                                     \\[+0.0em] \hline
\end{tabular}
\end{table}
\vspace*{\fill}




\clearpage




\subsubsection{Designated PC}
\label{SEC:preliminaryDecisions:selectionHardware:developmentPC:pc}

A 2015 Macbook Pro PC was selected as the designated development PC,
as this was available to the researcher
without the need to request additional funding.




\vspace{+2em}




\subsubsection{Designated Operating System}
\label{SEC:preliminaryDecisions:selectionHardware:developmentPC:os}

macOS was selected as the designated operating system,
as this was the only operating system installed on the designated PC.
{\fns(\tif{Version 10.12.5 was the most up to date version at the time of research.})}

\tbf{Alternative Operating System Compatibility}

Although the macOS operating system was used,
alternative operating systems {\fns(\tif{Windows and/or Linux})} would be equally acceptable.

Such a transition would primarily require an alternative Mathworks-supported compiler 
 \cite{REF:online:mathworks:supportedCompilers}
which would be compatible with the new operating system.
Slight alterations to the method of determining the test platform serial communication channel\iffalse, 
as described in Section~%
\ref{SEC:testPlatform:determiningSerialCommunicationChannel?}\fi
would also be required.

It is not expected that such a transition would be prohibitively difficult.




\clearpage




\subsubsection{Designated Hardware-Interfacing Software}
\label{SEC:preliminaryDecisions:selectionHardware:developmentPC:mathworks}

The Mathworks Software Suite was selected as the designated hardware-interfacing software due to:

\vspace{-0em}
\begin{itemize}[leftmargin=*]

\item Its first-party support for programming real-time hardware.

\item Its first-party support for simulating real-time hardware.

\item Its first-party driver support for Arduino-brand microcontrollers.

\item Its third-party driver support for the MinSeg.

\item Its first-party support for serial communication with hardware in real-time.

\item Its relatively user-friendly language and interfaces.

\item Its relative commonality among students and academic institutions.\\[+0.25em]
      \hspace*{\fill}{\fns$
      \begin{bmatrix*}[r]
      \text{\tif{The software environment was already relatively familiar to}}\\
      \text{\tif{the author and to the advising professor prior to performing this study.}}
      \end{bmatrix*}
      $}

\item Its relatively affordable cost. 
      \hspace*{\fill}{\fns[\tif{With respect to students and academic institutions.} \raisebox{-0.75ex}{\textasciitilde}\tif{\$150}]}.

\end{itemize}
\vspace{-1em}




\iffalse

\subsubsubsection{Supported Compiler}
\label{SEC:preliminaryDecisions:selectionHardware:developmentPC:mathworks:compiler}




\subsubsubsection{First-Party Support Packages}
\label{SEC:preliminaryDecisions:selectionHardware:developmentPC:mathworks:arduinoSupport}




\subsubsubsection{Third-Party Support Packages}
\label{SEC:preliminaryDecisions:selectionHardware:developmentPC:mathworks:minsegSupport}

who

where

how





\clearpage




\subsubsection{Arduino Interfacing}
\label{SEC:preliminaryDecisions:selectionHardware:developmentPC:arduinoInterfacing}




\subsubsubsection{Programming}




\subsubsubsection{Serial Communication}




\fi




\clearpage



\end{document}










